The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-15 methods/ms.tex
changed PCA figures and added new map demo figure

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.8]{eachpca}
    \end{center}
  \end{minipage}
\vspace{0.25in}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.8]{eachpca_20iters}
    \end{center}
  \end{minipage}
  \caption{{\it Top}: a grid of maps of the first 20 PCA components
displayed at the same scale.  It is clear that NCG 7538, the object
imaged, has correlated emission in each component.  There are varying
levels of correlated noise in each component, with the first through
third being the most obvious atmospheric components.  Most of the
other noise components are probably various bits of correlated
detector noise. {\it Bottom}: The same figure, but after 20
iterations.  The figure is the breakdown of the atmosphere remainder
(i.e. the raw data minus the astrophysical model) into eigenfunctions.
Very little astrophysical flux remains at any level of correlation,
though there is some at large (few arcminute) scales.}
\label{fig:PCA_Graphical}

@@

@@

% first millimeter....
The BGPS is the first (sub)millimeter survey of a substantial fraction
of the Galactic Plane, providing an unbiased look at the high-density
gas most intimately associated with the earliest phases of star
formation.  Inspection of Figure \ref{fig:BGPSMontage} shows excellent
correspondence with SCUBA maps of small sub-fields throughout the
plane \citep{difrancesco08}.  BGPS contours overlaid on the GLIMPSE
survey \citep{benjamin03} show excellent correlation with 8\mum\
infrared dark clouds (IRDCs).  However, many features in the BGPS maps
do not appear in the Spitzer observations, which suggests that the 1.1
mm emission traces dense clumps without a background to absorb.  A
study of IRDC correlation with BGPS emission is underway
\citep{battersby09}.

>>>>

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[angle=90,scale=0.6]{eachpca}
    \end{center}
  \end{minipage}
\vspace{0.25in}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[angle=90,scale=0.6]{eachpca_20iters}
    \end{center}
  \end{minipage}
  \caption{Selected images to illustrate the PCA process.  The displays are in
  Galactic coordinates with a color range from -.1 to 1.0 Jy/beam.
  {\it Top}: a grid of maps of the first 20 PCA components
displayed at the same scale.  It is clear that NCG 7538, the object
imaged, has correlated emission in each component.  There are varying
levels of correlated noise in each component, with the first through
third being the most obvious atmospheric components.  Most of the
other noise components are probably varieties of correlated
detector noise. {\it Bottom}: The same figure, but after 20
iterations.  The figure is the breakdown of the atmosphere remainder
(i.e. the raw data minus the astrophysical model) into eigenfunctions.
Very little astrophysical flux remains at any level of correlation,
though there is some at large (few arcminute) scales.}
\label{fig:PCA_Graphical}

@@

Five image types will be released, each covering the same regions.  The maps
are standard astrophysical maps subject to the caveats previously mentioned,
the most important being the spatial filtering function (section \ref{sec:}).
The model maps are deconvolved using the maximum-entropy method with kernels
specified in the header.  The residual map is the map of the model timestream
subtracted from the data timestream; it is close to but not identical to the
map minus the model.  The weightmap shows the inverse-variance weighting of
each pixel.  The nhitsmap shows how many recorded data points from the
timestream have been assigned to each pixel; it is proportional to the dwell
time per pixel (each 'hit' is .1s).  Examples of each (except the nhitsmap)
are given in figure \ref{fig:sampleimages}.

\Figure{image_types}{Examples of four of the image types being released.  Top
left: MAP.  Top right: Residual.  Bottom left: Deconvolved.  Bottom right:
Weight}{fig:sampleimages}{1.0}

@@

% first millimeter....
The BGPS is the first millimeter survey of a substantial fraction
of the Galactic Plane, providing an unbiased look at the high-density
gas most intimately associated with the earliest phases of star
formation.  Inspection of Figure \ref{fig:BGPSMontage} shows excellent
correspondence with SCUBA maps of small sub-fields throughout the
plane \citep{difrancesco08}.  BGPS contours overlaid on the GLIMPSE
survey \citep{benjamin03} show excellent correlation with 8\mum\
infrared dark clouds (IRDCs).  However, many features in the BGPS maps
do not appear in the Spitzer observations, which suggests that the 1.1
mm emission traces dense clumps without a background to absorb.  A
study of IRDC correlation with BGPS emission is underway
\citep{battersby09}.
